### 2013-08-15 Tex/chapters/model.tex
Christophs Verbesserungsvorschläge Umgesetzt, Form, Rechtschreibung

    The examined model is a modified 2D Ising model.

@@

    as the \emph{standard Ising model}, is a square lattice with edge length \(L\) and

@@

    nearest neighbors described by the Hamiltonian from Eq.\ \eqref{eq:hamiltonian}

@@

        H = - \sum_{\avg{i,j}}J_{ij}s_{i}s_{j} - \sum_i \tilde{H}_i s_i

@@

    neighbors. And \(J_{ij}\) is the coupling constant between \(i\) and
    \(j\). If \(J_{ij} > 0 \ \forall i,j\) the model resembles a ferromagnet.
    For the standard Ising model \(J_{ij}=1 \forall i,j\) applies.
    \(\tilde{H}_i\) denotes the outer magnetic field at the position of
    site \(i\). For the standard Ising model \(\tilde{H}_i=0 \ \forall i\)

@@

    The most important modification of the standard Ising modell in this

@@

    The displacement is randomly Gauß distributed with the standard

@@

    from a Gauß distribution Eq.\ \eqref{eq:gauss}.

@@

        f(x)=\frac{1}{\sqrt{2\pi}\sigma}\mathrm{e}^{-\frac{x^2}{2\sigma^2}}

@@

    This \(\sigma\) is also called \emph{disorder parameter} in the following.
    Because most sites will only have one nearest neighbor after the
    displacement, the lattice would collapse to many very small clusters.
    To avoid this, the new "nearest" neighbors are those sites connected
    by an edge. The edges are constructed according to

@@

    so that the lattice represents a proximity graph. Note that edges
    of a proximity graph do not cross each other, hence the 2D character
    of the lattice is preserved. The coupling constant \(J\) gets

@@

    The boundary is periodic e.g.\ nodes near the right edge can be

@@

    by edges which connect to an dashed node.

@@

    standard Ising model. For this exists an analytic solution \cite{Onsager1944} for the
    critical temperature

@@

    and \(\gamma = \frac{7}{4}\).\\

@@

    class of the standard Ising model, i.e.\ has the same critical

@@

\subsection{Gabriel- and Relative Neighborhood Graph}
\label{ssec:graphtypes}
    A graph \(G(V,E)\) is a set of nodes \(V\) and edges \(E\). In the
    scope of this model, the nodes get identified with the sites of the
    lattice and the edges signal the neighbor status of two sites. If the
    corresponding nodes are connected, the sites are neighbors.\\
    All here mentioned graph types are \emph{proximity graphs}. They are
    connecting nodes which are by some metric near to each other.
    Hence they are suited to generalize problems defined on regular
    lattices with nearest neighbor relationships, like the Ising model
    from the Sec.\ \ref{ssec:isingmodel}.
    In this thesis the distance is always determined by the Euclidean
    metric in two dimensions, though in principle every metric in any
    dimension can be used.\\

@@

    the product is of order \(O(N^3)\)\\

@@

    for each cell a list with nodes lying inside it like presented in

@@

    edge between the nodes. On the other hand nodes, that will be connected,

>>>>

    The examined model is a 2D Ising model.

@@

    as the \emph{square lattice Ising model}, is a square lattice with edge length \(L\) and

@@

    nearest neighbors described by the Hamiltonian

@@

        H = - \sum_{\avg{i,j}}J_{ij}s_{i}s_{j} - \sum_i h_i s_i.

@@

    neighbors, so that they are directly coupled to each other. The
    coupling between \(i\) and \(j\) is characterized by \(J_{ij}\),
    the coupling constant. If \(J_{ij} > 0 \ \forall i,j\) the model resembles a ferromagnet.
    For the square lattice Ising model \(J_{ij}=1 \forall i,j\) applies.
    \(h_i\) denotes the outer magnetic field at the position of
    site \(i\). For the square lattice Ising model \(h_i=0 \ \forall i\)

@@

    The most important modification of the square lattice Ising modell in this

@@

    The displacement is randomly Gaussian distributed with the standard

@@

    from a Gaussian distribution

@@

        f(x)=\frac{1}{\sqrt{2\pi}\sigma}\mathrm{e}^{-\frac{x^2}{2\sigma^2}}.

@@

    \(\sigma\) is also called \emph{disorder parameter} in the following.
    Most sites will only have one nearest neighbor after the
    displacement. If only the edges between these neighbors remain,
    the lattice would collapse to many very small clusters. But if one
    leaves the edges as the were before the displacement, the edges would
    cross -- at least for big displacements. The crossing of edges then
    would destroy the two dimensional character of the model and the results
    would not be compareable with known results for the two dimensional
    Ising model.
    To avoid this, a new edge set will be etablished after the displacement.
    The edges are constructed according to

@@

    so that the lattice represents a proximity graph. Edges
    of the used proximity graph do not cross each other, hence the 2D
    character of the lattice is preserved. The coupling constant \(J\) gets

@@

    The boundary is periodic, i.e.\ nodes near the right edge can be

@@

    by edges which connect a solid node to a dashed node.

@@

    square lattice Ising model. For this exists an analytic solution \cite{Onsager1944}.
    The critical temperature is

@@

    and \(\gamma = \frac{7}{4}\). These values are universal for the Ising
    model. Their meaning will be explained in Sec.\ \ref{ssec:critExp} in more detail.\\

@@

    class of the square lattice Ising model, i.e.\ has the same critical

@@

\subsection{Gabriel- and Relative Neighborhood Graph}
\label{ssec:graphtypes}
    A graph \(G(V,E)\) is a set of nodes \(V\) and edges \(E\). In the
    scope of this model, the nodes get identified with the sites of the
    lattice and the edges signal the neighbor status of two sites. If the
    corresponding nodes are connected, the sites are neighbors.\\
    All here mentioned graph types are \emph{proximity graphs}.
    The edges of these graphs connect nodes which are by some metric near
    to each other.
    Hence they are suited to generalize problems defined on regular
    lattices with nearest neighbor relationships.
    In this thesis the distance is always determined by the Euclidean
    metric in two dimensions, though in principle every metric in any
    dimension can be used.\\

@@

    the running time of a straight forward implementation would be of
    order \(O(N^3)\).\\

@@

    for each cell a list with nodes lying inside like presented in

@@

    edge between the nodes. On the other hand, nodes that will be connected
